---
title: "Analysis"
author: "April"
date: "September 7, 2017"
output: rmarkdown::github_document
---

This is a practice document for gitmd for the IFD repo.
TODO
Link this with the Setup data environment to create plots/figures to put in this rm file.
Change to gitmd output

#load data
#make a plot

```{r, setting up envr} 
#make this block silent
library(plyr)
library(ggplot2)
library(gridExtra)
library(pwr)
library(dplyr)

setwd("C:/Users/alpeterson7/Documents/HannahVR/HVRrepo")
data<- load("HVR_data_setup.RData")

new.data <- mergd_file_name %>% filter(!(IFD > 1000) )

```

## Header1, Summary of Interfocal Distances from a F2 Cross


#### Initial Stats


mouse specific tables to be used in plots. I should be able to add BD's data.
```{r, tables}
#mouse summary stats observations for each class
image_data <- ddply(new.data, .(file_name), summarize,
                        N_IFD = length(IFD),
                        ncells = max(Cell.Count),
                        prcnt_2CO = N_IFD / (ncells*19)
            #number of cells / number of IFDs = proxy for proportion of 2COs            
                        
)

mouse_data <- ddply(new.data, .(Animal.ID), summarize,
                        N_IFD = length(IFD),
                        ncells = max(Cell.Count),
                        prcnt_2CO = N_IFD / (ncells*19)
            #number of cells / number of IFDs = proxy for proportion of 2COs            
                        
)
#mouse_data the mouse data is displayed in a very long table
```

* histogram of IFD
```{r, histIFD}
#make sure outliers are removes
hh <- hist(new.data$IFD)#adjust the axis names

gg <- hist(new.data$nMLH1_foci)
hh
gg
```
The histogram appears normally distributed, but with a slight right tail.

#### Things to look at
* proportion of CO classes (per mouse)
* range of proportion classes
* mean and variation of IFD

* min value per F2 mouse
* normalized IFD **
* relationsihp of total SC and CO number
