---
title: "Analysis"
author: "April"
date: "September 7, 2017"
output: github_document
---

This is a practice document for gitmd for the IFD repo.
TODO
Link this with the Setup data environment to create plots/figures to put in this rm file.
Change to gitmd output


```{r, setting, echo = FALSE, include=FALSE} 
#make this block silent
library(plyr)
library(ggplot2)
library(gridExtra)
library(pwr)
library(dplyr)

setwd("C:/Users/alpeterson7/Documents/HannahVR/HVRrepo")
data<- load("HVR_data_setup.RData")

```

### Header1, Summary of Interfocal Distances from a F2 Cross


#### Initial Stats
- number of mice used

- mean and variance of MLH1 for each category (boxplots)

- mean and variance of IFD for each category

mouse specific tables to be used in plots. I should be able to add BD's data.
```{r, tables, echo=FALSE}
#mice used in each category (HVR and BD)
BD_mice_num <- ddply(BD_data, .(Cross), summarize,
                        N_mice = length(unique(ANIMAL_ID)), 
                     num_cells = length(nMLH1_foci)
)
  
HVR_mice_num <- ddply(data_HVR_full, .(Cross), summarize,
                        N_mice = length(unique(Animal.ID)), 
                     num_IFD = length(IFD)
)
HVR_mice_num
BD_mice_num
```
Not all of the PWD from HVR data overlap with the PWD in BD data set.



* histogram of IFD
(the echo= false ) still produces some output code.
```{r, histIFD, echo=FALSE}
#make sure outliers are removes
hh <- hist(IFD_nMLH1$IFD)#adjust the axis names

gg <- hist(IFD_nMLH1$nMLH1_foci)
hh
gg
```
The histogram appears normally distributed, but with a slight right tail.

#### Things to look at
* proportion of CO classes (per mouse)
* range of proportion classes
* mean and variation of IFD

* min value per F2 mouse
* normalized IFD **
* relationsihp of total SC and CO number
