---
title: "Analysis"
author: "April"
date: "September 7, 2017"
output: github_document
---

This is a practice document for gitmd for the IFD repo.
TODO
Link this with the Setup data environment to create plots/figures to put in this rm file.
Change to gitmd output


```{r, setting, echo = FALSE, include=FALSE} 
#make this block silent
library(plyr)
library(ggplot2)
library(gridExtra)
library(pwr)
library(dplyr)
library(mmod)

#setwd("C:/Users/alpeterson7/Documents/HannahVR/HVRrepo")
data<- load("HVR_data_setup.RData")
```

### Summary of Interfocal Distances from a F2 Cross

discription of the data and purpose of Analysis. BD data of MLH1 measures in meiotice cells. HVR measures of inter-focal distances of foci on the same bivalent. 

#### Patterns to look at
* proportion of CO classes (per mouse)
* range of proportion classes
* mean and variation of IFD
* min value per F2 mouse
* normalized IFD **
* relationsihp of total SC and CO number


These F2's were genrated to compared the average CO number per cell across two HM subspecies. Comparing the the average propotions of bivalent types (1CO, 2CO ect) per cell breaks down that phenotype one more level.
Approach; BD data, She filled out the proportions.

Since measuring the proportion of object classes from HVR's data would require the assumption that there are no 0COs, (which is not true), Useing BD's data will be more acurate. 
But the general approach of quantifying CO proportions from HVR data would be something like... 19 - ( length(IFD) - n3CO*2).

#### Initial Stats

```{r, tables, echo=FALSE}
#mice used in each category (HVR and BD)
BD_mice_num <- ddply(BD_data, .(Cross), summarize,
                        N_mice = length(unique(ANIMAL_ID)), 
                     num_cells = length(nMLH1_foci)
)
  
HVR_mice_num <- ddply(data_HVR_full, .(Cross), summarize,
                        N_mice = length(unique(Animal.ID)), 
                     num_IFD = length(IFD)
)
HVR_mice_num
BD_mice_num
```
(Not all of the PWD from HVR data overlap with the PWD in BD data set.)


```{r, histIFD, echo=FALSE}
#make sure outliers are removes
#seperate by mice, indicate the parental values

hh <- hist(IFD_nMLH1$IFD)#adjust the axis names


gg <- hist(IFD_nMLH1$nMLH1_foci)

```

The histogram appears normally distributed, but with a slight right tail.

#### Bivalent Class proportions table

BD's table has columns for the number of X0, 1X0, 2XO and 3XO. This can be used to calculate the average proportion of each object class. 

```{r, class_proportions, echo=FALSE, warning=FALSE}
BD_F2 <- BD_data[BD_data$Cross == "CxPF2", ]

BDmouseBivClass_proportions <- ddply(BD_F2, .(ANIMAL_ID), summarize,
                    nChr = sum(nChr-1),
                   nCells = length(nMLH1_foci),
                     biv0CO =mean( ((nChrWith0X) ),  na.rm=TRUE ),#this col is tricky, X or 1 number
                     biv1CO =mean( ((nChrWith1XO) ),  na.rm=TRUE ), 
                     biv2CO =mean( ((nChrWith2XO) ),  na.rm=TRUE ),
                     biv3CO =mean( ((nChrWith3.XO) ),  na.rm=TRUE )
                   
                  # varbiv0CO =var( (as.numeric(nChrWith0X) ) ),#this col is tricky, X or 1 number
              #       varbiv1CO =var( (as.numeric(nChrWith1XO) ) ), 
               #      varbiv2CO =var( (as.numeric(nChrWith2XO) ) ),
                #     varbiv3CO =var( (as.numeric(nChrWith3.XO) ) ),
                 #  varMLH1 = var(nMLH1_foci)
)
#BDmouseBivClass_proportions
#increase the denominator to nCells * 19
# should the proportions be compared to the MLH1 number?

# match these mice to the mice in IFD_MLH1, 
head(BDmouseBivClass_proportions)
tail(BDmouseBivClass_proportions)
```
#### visualizing proportions (under construction)

I want the 4 average proportions for each class inked in some way. 
scatter plot, line_range with points for each class, 
(examining acverage proportion of 0CO and average SC could provid a proxy for estimating CO maturity)

Strange observations:
 - F2's have a higher proportion of 2COs than 1COs
 - 3CO seem higher than they should be
 
Fixed
 - 0XO was fixed since orignal df had an inconsistant column

```{r, echo = FALSE}
#don't know why the plot below is broke
#plot(BDmouseBivClass_proportions$biv1CO, ylim=c(0, 50), col="black")#ylim=c(0, 0.1),
#points(BDmouseBivClass_proportions$biv2CO, ylim=c(0, 50), col="red")

groups <- plot( c(BDmouseBivClass_proportions$biv1CO,BDmouseBivClass_proportions$biv2CO, BDmouseBivClass_proportions$biv3CO),
      ylim=c(0, 20), col=c("black", "red", "blue") )

#points(BDmouseBivClass_proportions$biv1CO, col="blue")
#points(BDmouseBivClass_proportions$biv3CO, ylim=c(0, 50), col="orange")
#lines(BDmouseBivClass_proportions(ANIMAL_ID), pch=16)
groups
```

<the above plot isn't showing...>
The above plot, isnt exactly what I want but it shows the expected pattern for mean 1co,2co and 3co proportions. (Higher 1CO compared to 2CO)


black 0CO, blue 1CO, red 2CO, 3CO orange.
Points should follow the same vertical line for each mouse.

This plot displays a general pattern of 3CO bivs being rarer than 0CO bivs. 2COs are usually at a higher proportion than 1COs (F2s). Without linking all the proportions per mouse, this figure is not that useful.

```{r, include=FALSE}
#median raw 3CO numbers are all 2
BDmouseBivClass_proportions2 <- ddply(BD_F2, .(ANIMAL_ID), summarize,
                   #  Cross = as.factor(Cross),
                    nChr = sum(nChr-1),
                   nCells = length(nMLH1_foci),
                     biv0CO =median( (as.numeric(nChrWith0X)/nChr ) ),
                     biv1CO =median( (as.numeric(nChrWith1XO)/nChr ) ), 
                     biv2CO =median( (as.numeric(nChrWith2XO)/nChr ) ),
                     biv3CO =median( (as.numeric(nChrWith3.XO)/nChr ) ) 
)

#harmonic mean, 1/mean(1/a)
BDmouseBivClass_proportions3 <- ddply(BD_F2, .(ANIMAL_ID), summarize,
                   #  Cross = as.factor(Cross),
                    nChr = sum(nChr),
                   nCells = length(nMLH1_foci),
                     biv0CO =harmonic_mean( (as.numeric(nChrWith0X) ) ),
                     biv1CO =harmonic_mean( (as.numeric(nChrWith1XO) ) ), 
                     biv2CO =harmonic_mean( (as.numeric(nChrWith2XO) ) ),
                     biv3CO =harmonic_mean( (as.numeric(nChrWith3.XO) ) ) 
)

```

```{r, include = FALSE}
plot(BDmouseBivClass_proportions2$biv1CO, ylim=c(0, 0.1), col="black")

points(BDmouseBivClass_proportions2$biv0CO,ylim=c(0, 0.1), col="blue")

points(BDmouseBivClass_proportions2$biv2CO,ylim=c(0, 0.1), col="red")

points(BDmouseBivClass_proportions2$biv3CO,ylim=c(0, 0.1), col="orange")
```



#### Range and Minimums of IFD measures.

The following plots display the ranges of IFDs, the min and max distances between two foci. Check effects of 3COs. These data could skew the min IFD values. The current data frame, has a column with a counter of 3CO per cell. 

How could variation in min IFD values, play a role in regulation of IFD. 

There doesn't seem to be any relationship between min values and the range. There might be a relationship with the number of measurements. 


```{r, echo=FALSE}

P0 <- IFD_nMLH1[(IFD_nMLH1$Cross.x == "CAST" | IFD_nMLH1$Cross.x == "PWD"), ]
F2 <- IFD_nMLH1[IFD_nMLH1$Cross.x == "CxPF2", ]

#make F2 mouse data table (with min and max)
F2_table <- ddply(F2, .(Animal.ID), summarise,
              total_ifd =  length(IFD),
              mean_IFD = mean(IFD), 
              min = min(IFD),
              max = max(IFD),
              range = max-min,
              var= var(IFD)
)
#F2_table <- F2_table[order(F2_table$range),]
#order.range <- order(F2_table$range)
#F2_table<- F2_table[order.range, ]

rr <- ggplot(F2_table, aes(x = reorder(Animal.ID, range), y = mean_IFD)) +  geom_linerange(aes(ymin = min, ymax =max)) + ggtitle("F2 variation in IFD ranges") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
rr

mm <- ggplot(F2_table, aes(x = reorder(Animal.ID, -min), y = mean_IFD)) +  geom_linerange(aes(ymin = min, ymax =max)) +ggtitle("F2 variation in Minimum IFD values") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
mm

vv <- ggplot(F2_table, aes(x = reorder(Animal.ID, var), y = mean_IFD)) +  geom_linerange(aes(ymin = min, ymax =max)) + ggtitle("F2 variation in IFD variance") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
vv
```

Parental versions
```{r, echo=FALSE}
P0 <- IFD_nMLH1[(IFD_nMLH1$Cross.x == "CAST" | IFD_nMLH1$Cross.x == "PWD"), ]

P0_table <- ddply(P0, .(Animal.ID), summarise,
              total_ifd =  length(IFD),
              mean_IFD = mean(IFD), 
              min = min(IFD),
              max = max(IFD),
              range = max-min,
              var= var(IFD)
)

pp <- ggplot(P0_table, aes(x = reorder(Animal.ID, range), y = mean_IFD)) +  geom_linerange(aes(ymin = min, ymax =max)) + ggtitle("P0 variation in IFD ranges") + theme(axis.title.x=element_blank())
pp

```